---
title: 'IMT paper: Bayes Factors'
author: "Thomas"
date: "7/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tim suggests using Bayes Factors on all so-called "null findings" to determine the evidence for the null.

### The primary outcome statistic is the correlation between predicted and observed IMT. 

### Use the "BayesFactor" package to compute BF for each correlation and generate output.
### Follow steps in (https://richarddmorey.github.io/BayesFactor/#lincor) 

### I don't know how to interpret output - Tim and Javi, please help.

```{r message = F}
library(BayesFactor)
library(ggplot2)
library(R.matlab)
library(sjPlot)
```

## OldFaces (PFA stimulus set) - wholebrain pattern

Load data:
```{r}
mat = readMat('~/Box/@Predict_IMT/Faces/OF/AllFaces/data.mat')
imt = data.frame(observed = mat$out[[7]], predicted = mat$out[[8]])
```

Replicate correlation and scatterplot:
```{r fig.width = 4, fig.height = 4}
cor.test(imt$predicted, imt$observed)
ggplot(imt, aes(x = predicted, y = observed)) + geom_point() + 
  geom_smooth(method = lm, colour = 'black') + theme_classic() +
  labs(x = "Predicted CA-IMT (mm)", y = "Observed CA-IMT (mm)") + 
  theme(text = element_text(size = 14))
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#lincor):
```{r}
bf = correlationBF(y = imt$observed, x = imt$predicted)
bf
samples = posterior(bf, iterations = 10000)
summary(samples)
plot(samples[,"rho"])
```

## OldFaces (PFA stimulus set) - amygdala ROI

Load data:
```{r}
mat = readMat('~/Box/@Predict_IMT/Faces/OF/AllFaces/amygdala/data.mat')
imt = data.frame(observed = mat$out[[7]], predicted = mat$out[[8]])
```

Replicate correlation and scatterplot:
```{r fig.width = 4, fig.height = 4}
cor.test(imt$predicted, imt$observed)
ggplot(imt, aes(x = predicted, y = observed)) + geom_point() + 
  geom_smooth(method = lm, colour = 'black') + theme_classic() +
  labs(x = "Predicted CA-IMT (mm)", y = "Observed CA-IMT (mm)") + 
  theme(text = element_text(size = 14))
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#lincor):
```{r}
bf = correlationBF(y = imt$observed, x = imt$predicted)
bf
samples = posterior(bf, iterations = 10000)
summary(samples)
plot(samples[,"rho"])
```

## OldFaces (PFA stimulus set) - amygdala lesion

Load data:
```{r}
mat = readMat('~/Box/@Predict_IMT/Faces/OF/AllFaces/amygdala_lesion/data.mat')
imt = data.frame(observed = mat$out[[7]], predicted = mat$out[[8]])
```

Replicate correlation and scatterplot:
```{r fig.width = 4, fig.height = 4}
cor.test(imt$predicted, imt$observed)
ggplot(imt, aes(x = predicted, y = observed)) + geom_point() + 
  geom_smooth(method = lm, colour = 'black') + theme_classic() +
  labs(x = "Predicted CA-IMT (mm)", y = "Observed CA-IMT (mm)") + 
  theme(text = element_text(size = 14))
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#lincor):
```{r}
bf = correlationBF(y = imt$observed, x = imt$predicted)
bf
samples = posterior(bf, iterations = 10000)
summary(samples)
plot(samples[,"rho"])
```

## OldFaces - PINES

Load data:
```{r}
imt = read.csv('~/Box/@Predict_IMT/Generalizability/predicted_observed_pattern-PINES_contrasts-OF.csv')
colnames(imt) = c('predicted', 'observed')
```

Replicate correlation and scatterplot:
```{r fig.width = 4, fig.height = 4}
cor.test(imt$predicted, imt$observed)
ggplot(imt, aes(x = predicted, y = observed)) + geom_point() + 
  geom_smooth(method = lm, colour = 'black') + theme_classic() +
  labs(x = "Predicted CA-IMT (mm)", y = "Observed CA-IMT (mm)") + 
  theme(text = element_text(size = 14))
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#lincor):
```{r}
bf = correlationBF(y = imt$observed, x = imt$predicted)
bf
samples = posterior(bf, iterations = 10000)
summary(samples)
plot(samples[,"rho"])
```

## NewFaces (NIM-STIM stimulus set) - wholebrain pattern

Load data:
```{r}
mat = readMat('~/Box/@Predict_IMT/Faces/NF/AllFaces/data.mat')
imt = data.frame(observed = mat$out[[7]], predicted = mat$out[[8]])
```

Replicate correlation and scatterplot:
```{r fig.width = 4, fig.height = 4}
cor.test(imt$predicted, imt$observed)
ggplot(imt, aes(x = predicted, y = observed)) + geom_point() + 
  geom_smooth(method = lm, colour = 'black') + theme_classic() +
  labs(x = "Predicted CA-IMT (mm)", y = "Observed CA-IMT (mm)") + 
  theme(text = element_text(size = 14))
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#lincor):
```{r}
bf = correlationBF(y = imt$observed, x = imt$predicted)
bf
samples = posterior(bf, iterations = 10000)
summary(samples)
plot(samples[,"rho"])
```

### Did not look at NewFaces amygdala ROI / amygdala lesion because the wholebrain pattern did not sufficiently predict IMT.

## IAPS - wholebrain pattern

Load data:
```{r}
mat = readMat('~/Box/@Predict_IMT/IAPS/data.mat')
imt = data.frame(observed = mat$out[[7]], predicted = mat$out[[8]])
```

Replicate correlation and scatterplot:
```{r fig.width = 4, fig.height = 4}
cor.test(imt$predicted, imt$observed)
ggplot(imt, aes(x = predicted, y = observed)) + geom_point() + 
  geom_smooth(method = lm, colour = 'black') + theme_classic() +
  labs(x = "Predicted CA-IMT (mm)", y = "Observed CA-IMT (mm)") + 
  theme(text = element_text(size = 14))
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#lincor):
```{r}
bf = correlationBF(y = imt$observed, x = imt$predicted)
bf
samples = posterior(bf, iterations = 10000)
summary(samples)
plot(samples[,"rho"])
```

## IAPS - amygdala ROI
**NOTE** this produces a misleadingly strong negative correlation due to failure to generate a pattern (i.e., LASSO shrinks all predictors) in 1 of the 2 outer folds. 

Load data:
```{r}
mat = readMat('~/Box/@Predict_IMT/IAPS/amygdala/data.mat')
imt = data.frame(observed = mat$out[[7]], predicted = mat$out[[8]])
```

Replicate correlation and scatterplot:
```{r fig.width = 4, fig.height = 4}
cor.test(imt$predicted, imt$observed)
ggplot(imt, aes(x = predicted, y = observed)) + geom_point() + 
  geom_smooth(method = lm, colour = 'black') + theme_classic() +
  labs(x = "Predicted CA-IMT (mm)", y = "Observed CA-IMT (mm)") + 
  theme(text = element_text(size = 14))
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#lincor):
```{r}
bf = correlationBF(y = imt$observed, x = imt$predicted)
bf
samples = posterior(bf, iterations = 10000)
summary(samples)
plot(samples[,"rho"])
```

## IAPS - amygdala lesion

Load data:
```{r}
mat = readMat('~/Box/@Predict_IMT/IAPS/amygdala_lesion/data.mat')
imt = data.frame(observed = mat$out[[7]], predicted = mat$out[[8]])
```

Replicate correlation and scatterplot:
```{r fig.width = 4, fig.height = 4}
cor.test(imt$predicted, imt$observed)
ggplot(imt, aes(x = predicted, y = observed)) + geom_point() + 
  geom_smooth(method = lm, colour = 'black') + theme_classic() +
  labs(x = "Predicted CA-IMT (mm)", y = "Observed CA-IMT (mm)") + 
  theme(text = element_text(size = 14))
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#lincor):
```{r}
bf = correlationBF(y = imt$observed, x = imt$predicted)
bf
samples = posterior(bf, iterations = 10000)
summary(samples)
plot(samples[,"rho"])
```


## IAPS - PINES

Load data:
```{r}
imt = read.csv('~/Box/@Predict_IMT/Generalizability/predicted_observed_pattern-PINES_contrasts-IAPS.csv')
colnames(imt) = c('predicted', 'observed')
```

Replicate correlation and scatterplot:
```{r fig.width = 4, fig.height = 4}
cor.test(imt$predicted, imt$observed)
ggplot(imt, aes(x = predicted, y = observed)) + geom_point() + 
  geom_smooth(method = lm, colour = 'black') + theme_classic() +
  labs(x = "Predicted CA-IMT (mm)", y = "Observed CA-IMT (mm)") + 
  theme(text = element_text(size = 14))
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#lincor):
```{r}
bf = correlationBF(y = imt$observed, x = imt$predicted)
bf
samples = posterior(bf, iterations = 10000)
summary(samples)
plot(samples[,"rho"])
```


# New - BF for linear regressions (age, sex, CMR)

## OldFaces (PFA stimulus set) 

### Does pattern predict above and beyond covariates?

Load data:
```{r}
imt = read.csv('~/Box/@Predict_IMT/Faces/OF/AllFaces/cmr/data_withCMR.csv')
```

Replicate regression:
```{r fig.width = 4, fig.height = 4}
fit1 = lm(IMT_observed ~ age + sex + CMR, data = imt)
fit2 = lm(IMT_observed ~ age + sex + CMR + IMT_predicted, data = imt)
tab_model(fit1, fit2, show.std = T, show.ci = F, show.se = T, show.est = F)
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#glm):
```{r}
full = lmBF(IMT_observed ~ age + sex + CMR + IMT_predicted, data = imt)
noBrain = lmBF(IMT_observed ~ age + sex + CMR, data = imt)
brainOnly = lmBF(IMT_observed ~ IMT_predicted, data = imt)
allBFs = c(full, noBrain, brainOnly)
allBFs
full / noBrain
```

### Does age, sex, or CMR modify prediction?

### AGE

Replicate regression:
```{r fig.width = 4, fig.height = 4}
imt$ageint = scale(imt$age, scale = F)*scale(imt$IMT_predicted, scale = F)
fit1 = lm(IMT_observed ~ age + IMT_predicted, data = imt)
fit2 = lm(IMT_observed ~ age + IMT_predicted + ageint, data = imt)
tab_model(fit1, fit2, show.std = T, show.ci = F, show.se = T, show.est = F)
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#glm):
```{r}
full = lmBF(IMT_observed ~ age + IMT_predicted + ageint, data = imt)
noInteraction = lmBF(IMT_observed ~ age + IMT_predicted, data = imt)
allBFs = c(full, noInteraction)
allBFs
full / noInteraction
```

### SEX

Replicate regression:
```{r fig.width = 4, fig.height = 4}
imt$sexint = scale(imt$sex, scale = F)*scale(imt$IMT_predicted, scale = F)
fit1 = lm(IMT_observed ~ sex + IMT_predicted, data = imt)
fit2 = lm(IMT_observed ~ sex + IMT_predicted + sexint, data = imt)
tab_model(fit1, fit2, show.std = T, show.ci = F, show.se = T, show.est = F)
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#glm):
```{r}
full = lmBF(IMT_observed ~ sex + IMT_predicted + sexint, data = imt)
noInteraction = lmBF(IMT_observed ~ sex + IMT_predicted, data = imt)
allBFs = c(full, noInteraction)
allBFs
full / noInteraction
```

### CMR

Replicate regression:
```{r fig.width = 4, fig.height = 4}
imt$cmrint = scale(imt$CMR, scale = F)*scale(imt$IMT_predicted, scale = F)
fit1 = lm(IMT_observed ~ CMR + IMT_predicted, data = imt)
fit2 = lm(IMT_observed ~ CMR + IMT_predicted + cmrint, data = imt)
tab_model(fit1, fit2, show.std = T, show.ci = F, show.se = T, show.est = F)
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#glm):
```{r}
full = lmBF(IMT_observed ~ CMR + IMT_predicted + cmrint, data = imt)
noInteraction = lmBF(IMT_observed ~ CMR + IMT_predicted, data = imt)
allBFs = c(full, noInteraction)
allBFs
full / noInteraction
```

## IAPS

### Does pattern predict above and beyond covariates?

Load data:
```{r}
imt = read.csv('~/Box/@Predict_IMT/IAPS/cmr/data_withCMR.csv')
```

Replicate regression:
```{r fig.width = 4, fig.height = 4}
fit1 = lm(IMT_observed ~ age + sex + CMR, data = imt)
fit2 = lm(IMT_observed ~ age + sex + CMR + IMT_predicted, data = imt)
tab_model(fit1, fit2, show.std = T, show.ci = F, show.se = T, show.est = F)
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#glm):
```{r}
full = lmBF(IMT_observed ~ age + sex + CMR + IMT_predicted, data = imt)
noBrain = lmBF(IMT_observed ~ age + sex + CMR, data = imt)
brainOnly = lmBF(IMT_observed ~ IMT_predicted, data = imt)
allBFs = c(full, noBrain, brainOnly)
allBFs
full / noBrain
```

### Does age, sex, or CMR modify prediction?

### AGE

Replicate regression:
```{r fig.width = 4, fig.height = 4}
imt$ageint = scale(imt$age, scale = F)*scale(imt$IMT_predicted, scale = F)
fit1 = lm(IMT_observed ~ age + IMT_predicted, data = imt)
fit2 = lm(IMT_observed ~ age + IMT_predicted + ageint, data = imt)
tab_model(fit1, fit2, show.std = T, show.ci = F, show.se = T, show.est = F)
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#glm):
```{r}
full = lmBF(IMT_observed ~ age + IMT_predicted + ageint, data = imt)
noInteraction = lmBF(IMT_observed ~ age + IMT_predicted, data = imt)
allBFs = c(full, noInteraction)
allBFs
full / noInteraction
```

### SEX

Replicate regression:
```{r fig.width = 4, fig.height = 4}
imt$sexint = scale(imt$sex, scale = F)*scale(imt$IMT_predicted, scale = F)
fit1 = lm(IMT_observed ~ sex + IMT_predicted, data = imt)
fit2 = lm(IMT_observed ~ sex + IMT_predicted + sexint, data = imt)
tab_model(fit1, fit2, show.std = T, show.ci = F, show.se = T, show.est = F)
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#glm):
```{r}
full = lmBF(IMT_observed ~ sex + IMT_predicted + sexint, data = imt)
noInteraction = lmBF(IMT_observed ~ sex + IMT_predicted, data = imt)
allBFs = c(full, noInteraction)
allBFs
full / noInteraction
```

### CMR

Replicate regression:
```{r fig.width = 4, fig.height = 4}
imt$cmrint = scale(imt$CMR, scale = F)*scale(imt$IMT_predicted, scale = F)
fit1 = lm(IMT_observed ~ CMR + IMT_predicted, data = imt)
fit2 = lm(IMT_observed ~ CMR + IMT_predicted + cmrint, data = imt)
tab_model(fit1, fit2, show.std = T, show.ci = F, show.se = T, show.est = F)
```

Compute BF as in (https://richarddmorey.github.io/BayesFactor/#glm):
```{r}
full = lmBF(IMT_observed ~ CMR + IMT_predicted + cmrint, data = imt)
noInteraction = lmBF(IMT_observed ~ CMR + IMT_predicted, data = imt)
allBFs = c(full, noInteraction)
allBFs
full / noInteraction
```